On Secure Delegation of SampBQP with a Classical Client

### 2020-02-05 hamiltonian.tex
Change thm env

\hannote{citation}
\begin{theorem}
	Given a circuit $C$ and classical input $x$, a $\BPP$ machine can reduce it to another circuit $C'$ and classical input $x'$, where $C'$ contains only Hadamard and Toffoli gates.
\end{theorem}

@@

\begin{theorem}
	Let $C$ be a circuit consisting of $T$ Hadamard or Toffoli gates. For any input string $x$,  there exists a local Hamiltonian $H_{C(x)}$  with the following properties:
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms
		\item $H_{C(x)}$ has a unique ground state  $\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$ with eigenvalue $0$. We call the first register of $\ket{\psi_{C(x)}}$ the data register, and the second register of $\ket{\psi_{C(x)}}$ the time register.
		\item For any state $\ket\phi$ such that $\braket{\phi|\psi_{C(x)}}=0$,  $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
	\end{itemize}

	Furthermore, there exists a $\BPP$ machine that can construct a description of $H_{C(x)}$ in polynomial time.
\end{theorem}

@@

\begin{theorem}
	Given a circuit $C$ consisting of Hadamard and Toffoli gates and an input string $x$, there exists a $\BPP$ machine that can construct a description of $H_{C(x)}$ in polynomial time.
\end{theorem}
\fi

\begin{theorem}
	Given circuit $C$ consisting of Hadamard and Toffoli gates and an input string $x\in\set{0,1}^*$, there exists an quantum algorithm that accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$. In particular, it accepts the $\ket{psi_{C(x)}}$ with probability $\fot$. Furthermore, this algorithm doesn't apply any quantum gates, using only $X$ and $Z$ measurements.
\end{theorem}

@@

\begin{theorem}
	Let $C$ be a circuit that:
	\begin{itemize}
		\item consists of either $H$ or $\Lambda(P(i))$, and the number of gates is $T$.\hannote{confusing?}
		\item uses $n$ qubits
	\end{itemize}
	Then a classical machine given $C$ can compute a circuit $C'$ that:
	\begin{itemize}
		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$ \hannote{don't like this notation}.
		\item uses $n+1$ qubits
		\item Let $x\in\set{0,1}^n$. Let $x|| 0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
		The measurement result of a tensor product of $X$ and $Z$ operators on the first $n$ qubits of $C'(x||0)$ has the same distribution as that on $C(x)$.
	\end{itemize}
\end{theorem}

@@

\begin{theorem}
	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$ with $O(1)$ nonzero components.
\end{theorem}

@@

\begin{theorem}
	Let $C=U_T\ldots U_1$ be a circuit consisting of Hadamard and Toffoli gates, and let $x\in\set{0, 1}^n$. Then there exists a $\BPP$  machine which generates the  description of a $H_{C(x)}\in\spn\mathcal{G}_{XZ}$ such that:
	\begin{itemize}
		\item its unique ground state is $$\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
		\item $\braket{\psi_{C(x)}|H_{C(x)}|\psi_{C(x)}}=0$
		\item $\forall\ket\phi,\braket{\phi|\psi_{C(x)}}=0\Rightarrow\braket{\phi|H_{C(x)}|\phi}\geq\frac{3}{4}$
		\item $H_{C(x)}$ has $O(T)$ nonzero terms whose coefficients are  at most $O(T^3)$.
	\end{itemize}
\end{theorem}

@@

\begin{theorem}\label{ThmXZCheck}
	Let $H$ have $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
	Then \autoref{AlgGroundStateCheck} accepts $\ket\phi$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$.
\end{theorem}
\begin{proof}

>>>>

\hannote{citation}
\begin{thm}
	Given a circuit $C$ and classical input $x$, a $\BPP$ machine can reduce it to another circuit $C'$ and classical input $x'$, where $C'$ contains only Hadamard and Toffoli gates.
\end{thm}

@@

\begin{thm}
	Let $C$ be a circuit consisting of $T$ Hadamard or Toffoli gates. For any input string $x$,  there exists a local Hamiltonian $H_{C(x)}$  with the following properties:
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms
		\item $H_{C(x)}$ has a unique ground state  $\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$ with eigenvalue $0$. We call the first register of $\ket{\psi_{C(x)}}$ the data register, and the second register of $\ket{\psi_{C(x)}}$ the time register.
		\item For any state $\ket\phi$ such that $\braket{\phi|\psi_{C(x)}}=0$,  $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
	\end{itemize}

	Furthermore, there exists a $\BPP$ machine that can construct a description of $H_{C(x)}$ in polynomial time.
\end{thm}

@@

\begin{thm}
	Given a circuit $C$ consisting of Hadamard and Toffoli gates and an input string $x$, there exists a $\BPP$ machine that can construct a description of $H_{C(x)}$ in polynomial time.
\end{thm}
\fi

\begin{thm}
	Given circuit $C$ consisting of Hadamard and Toffoli gates and an input string $x\in\set{0,1}^*$, there exists an quantum algorithm that accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$. In particular, it accepts the $\ket{psi_{C(x)}}$ with probability $\fot$. Furthermore, this algorithm doesn't apply any quantum gates, using only $X$ and $Z$ measurements.
\end{thm}

@@

\begin{thm}
	Let $C$ be a circuit that:
	\begin{itemize}
		\item consists of either $H$ or $\Lambda(P(i))$, and the number of gates is $T$.\hannote{confusing?}
		\item uses $n$ qubits
	\end{itemize}
	Then a classical machine given $C$ can compute a circuit $C'$ that:
	\begin{itemize}
		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$ \hannote{don't like this notation}.
		\item uses $n+1$ qubits
		\item Let $x\in\set{0,1}^n$. Let $x|| 0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
		The measurement result of a tensor product of $X$ and $Z$ operators on the first $n$ qubits of $C'(x||0)$ has the same distribution as that on $C(x)$.
	\end{itemize}
\end{thm}

@@

\begin{thm}
	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$ with $O(1)$ nonzero components.
\end{thm}

@@

\begin{thm}
	Let $C=U_T\ldots U_1$ be a circuit consisting of Hadamard and Toffoli gates, and let $x\in\set{0, 1}^n$. Then there exists a $\BPP$  machine which generates the  description of a $H_{C(x)}\in\spn\mathcal{G}_{XZ}$ such that:
	\begin{itemize}
		\item its unique ground state is $$\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
		\item $\braket{\psi_{C(x)}|H_{C(x)}|\psi_{C(x)}}=0$
		\item $\forall\ket\phi,\braket{\phi|\psi_{C(x)}}=0\Rightarrow\braket{\phi|H_{C(x)}|\phi}\geq\frac{3}{4}$
		\item $H_{C(x)}$ has $O(T)$ nonzero terms whose coefficients are  at most $O(T^3)$.
	\end{itemize}
\end{thm}

@@

\begin{thm}\label{ThmXZCheck}
	Let $H$ have $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
	Then \autoref{AlgGroundStateCheck} accepts $\ket\phi$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$.
\end{thm}
\begin{proof}
